saycam goldset analysis

### 2021-04-16 analysis/analysis_goldset.Rmd
update goldset exploratory script --> new filenames

### Get video/frame info from full cleaned dataset (saved)
# load('../data/openpose_detections_filtered.RData')
# vid_info <- d_all %>%
#   select(vid_name, frame, age_days, child_id)
# save(vid_info, file = '../data/vid_info.RData')

load('../data/vid_info.RData')
load('../data/ketan_gold_sample.RData')
```

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get videos that are flipped, i.e., 
flipped_videos <- right_side_up %>%
  filter(right_side_up==1) %>%
  rename(vid_name = video)
```

### Load SAYCAM metadata from csv file; get metadata from detections .csv
```{r}
metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"
meta=read.csv(metadata_file) %>%
  rowwise() %>%
  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))

@@

### Import bounding boxes for goldset & preprocess: filter videos, gather metadata, convert to pixel coordinates
```{r}
bounding_boxes = "../data/gold_sample_bounding_boxes.csv" 
height_px = 480; width_px = 640

bb = read.csv(bounding_boxes) %>%
  rowwise() %>%
  mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
  filter(!vid_name %in% flipped_videos$vid_name) %>%
  left_join(vid_info) %>%
  mutate(height_y = height*height_px, width_x = width*width_px, area = (height_y*width_x)/(height_px*width_px)) 
```
### Read in turk segmentations to get child vs. adult hands
```{r}
turk_annotations_seg = "../data/turk_segmentations_hands_only_processed.csv" 
g_seg = read.csv(turk_annotations_seg) %>%
  select(-HITID, -HITTypeId, -WorkerID)

@@

## Analyze basics from bounding boxes on goldset
### Preprocess bb data
```{r}
bb <- bb %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  mutate(x_pos = left*width_px, y_pos = top*height_px) %>%
  mutate(center_x = x_pos + width_x/2, center_y = y_pos - height_y/2) %>%
  filter(!is.na(child_id))

bb_forheatmap <- bb %>%
  filter(height>0)
```

@@

bb_check <- bb_all %>%
  mutate(frame_ind = frame, vid_name_short = vid_name) %>%
  left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
  filter(!is.na(full_image_path)) %>%
  filter(mean_confidence > 0)

# dir.create(paste0('bbcheck/'))
unique_images <- bb_check$full_image_path[300:350]

bb_check_face_tall <- bb_check_face %>%
  filter(top>.7) %>%
  filter(label=='face')

bb_check_weird_vids <- bb_check %>%
  filter(vid_name %in% weird_vids)

unique_images = unique(bb_check_weird_vids$full_image_path)
for (image in unique_images){
  this_image_rgb <- image_read(image)
  img <- image_draw(this_image_rgb)
  a <- bb_check %>%
    filter(full_image_path %in% image)

  # rect(a$x_pos, a$y_pos-a$height_y, a$x_pos+a$width_x, a$y_pos)

  text(a$left*680, a$top*480, a$top)

  annotated_file = paste0('bbcheck_sanity/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-center.jpg')
  image_write(img, annotated_file)
  dev.off()
}

@@

>>>>

## Get video/frame info from full cleaned dataset (saved)
# load('../data/preprocessed_data/openpose_detections_filtered_2020-01-29.RData')
# vid_info <- d_all %>%
  # select(vid_name, frame, age_days, child_id)
# save(vid_info, file = '../data/preprocessed_data/vid_info.RData')
load('../data/preprocessed_data/vid_info.RData')

# load('../data/raw_data/vid_info.RData')
load('../data/raw_data/ketan_gold_sample.RData')
```

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/raw_data/SAYCAM_allocentric_videos.csv"
right_side_up =read.csv(right_side_up_file)

# get videos that are flipped, i.e., 
flipped_videos <- right_side_up %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

### Load SAYCAM metadata from csv file; get metadata from detections .csv
```{r}
metadata_file = "../data/raw_data/Metadata_SAYcam-2019-12-0922_54_28.csv"
meta=read.csv(metadata_file) %>%
  rowwise() %>%
  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))

@@

### Import bounding boxes for goldset & preprocess: filter videos, gather metadata, convert to pixel coordinates
```{r}
bounding_boxes = "../data/raw_data/gold_sample_bounding_boxes.csv" 
height_px = 480; width_px = 640

bb = read.csv(bounding_boxes) %>%
  rowwise() %>%
  mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
  filter(!vid_name %in% flipped_videos$vid_name) %>%
  left_join(vid_info) %>%
  mutate(height_y = height*height_px, width_x = width*width_px, area = (height_y*width_x)/(height_px*width_px)) 
```
### Read in turk segmentations to get child vs. adult hands
```{r}
turk_annotations_seg = "../data/turk_data/turk_segmentations_hands_only_processed.csv" 
g_seg = read.csv(turk_annotations_seg) %>%
  select(-HITID, -HITTypeId, -WorkerID)

@@

## Analyze basics from bounding boxes on goldset
### Preprocess bb data
```{r}
bb <- bb %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  mutate(x_pos = left*width_px, y_pos = top*height_px) %>%
  mutate(center_x = x_pos + width_x/2, center_y = y_pos - height_y/2) 
  filter(!is.na(child_id))

# bb_forheatmap <- bb %>%
  # filter(height>0)
```

@@

bb_check <- bb %>%
  mutate(frame_ind = frame, vid_name_short = vid_name) %>%
  left_join(g_seg_info, by=c("vid_name_short","frame_ind")) %>%
  filter(!is.na(full_image_path)) %>%
  filter(mean_conf > 0)

dir.create(paste0('bbcheck_height/'))
# unique_images <- bb_check$full_image_path[300:350]

bb_check_subset <- bb_check %>%
  filter(height>.8) %>%
  filter(label=='hand')

unique_images = unique(bb_check_subset$full_image_path)
for (image in unique_images){
  this_image_rgb <- image_read(image)
  img <- image_draw(this_image_rgb)
  a <- bb_check %>%
    filter(full_image_path %in% image)

  rect(a$x_pos, a$y_pos, a$x_pos+a$width_x, a$y_pos - a$height)
  # text(a$x_pos*680, a$y_pos*480, a$top)
  # text(a$x_pos*680, a$y_pos*480, a$y_pos)
  annotated_file = paste0('bbcheck_height/',unique(a$vid_name_short), unique(a$frame_ind), 'OP-big-hands.jpg')
  image_write(img, annotated_file)
  dev.off()
}

@@

```{r}
bb_hand_only <- bb_SA %>%
  filter(label=='hand') 
  # filter(height<.6)

bb_face_only <- bb_SA %>%
  filter(label=='face')

# ggplot(bb_hand_only, aes(x=left, y=top)) +
#   geom_point() + 
#   stat_density_2d(aes(fill = ..level..), geom="polygon") +
#   coord_fixed(ratio=1) +
#   ggtitle('Hands')
